Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-24 mu/article/article.tex
Writin article.

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage{color}
% \usepackage{showframe}
% \usepackage[inline]{showlabels}

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \label{fig:alt-vx}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \label{fig:alt-vy}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
    \label{fig:alt-vx-comp-rtp}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
    \label{fig:alt-vy-comp-rtp}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{alt} structure. Both maxima where obtained for a polarization
    angle $\alpha=145^{\circ}$. }
    \label{fig:alt-vab-xy-comp-rtp}
\end{figure}

For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the absolute maximum response having for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
%
From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 
%
We also found that the absolute maximum of the response is obtained for a
polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
depicted in Fig. \ref{fig:alt-vx-comp-rtp} and the decomposition of
$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
\ref{fig:alt-vy} for this polarization angle.
%
Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
contribute with almost the same intensity giving a total spin-velocity near to
30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
component resulting in a spin-velocity near to 20\,Km/s.
%
Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.
%
Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
lesser contribution than $yz$ but for the energy range all three components
have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
both cases.
%
Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
the same spin polarization for all this range.}

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage{color}
% \usepackage{showframe}
\usepackage[inline]{showlabels}

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vy-comp-rtp}]
    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{alt} structure. Both maxima where obtained for a polarization
    angle $\alpha=145^{\circ}$. }
    \label{fig:alt-vab-comp-rtp}
\end{figure}

For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the absolute maximum response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
From Fig. \ref{fig:alt-3d-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 
% %%%%%%%%%%%%%%%%
% %% Starting description of ALT |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%
We also found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha = 145^{\circ}$. 
%
In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
\ref{fig:alt-vy-comp-rtp} we present the results for
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the photon
energy and the corresponding azimuthal $\theta$ and polar $\varphi$ angles.
%
Also in the bottom frames of Figs. \ref{fig:alt-vx-comp-rtp} and 
%
\ref{fig:alt-vy-comp-rtp} we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$ and
$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
$\mathcal{V}^{\mathrm{yz}}$ components for the fixed polarization angle.
% %%%%%%%%%%%%%%%%
% %% Description of ALT |V^{x}|, components and RTP
% %%%%%%%%%%%%%%%%
Making the analysis for the components and angles for
$|\mathcal{V}^{\mathrm{x}}|$ we can see that for the energy range from 0.70\,eV
to 0.74\,eV all the $xx$, $xy$, and $xz$ components contribute with almost the
same intensity giving a total spin-velocity near to 30\,Km/s and spin angles
$\theta$ and $\varphi$ near to $45.8^{\circ}$ and $40.7^{\circ}$, respectively.
%
In the other hand, for the energy range from 0.88\,eV to 0.95\,eV there is a
major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$ component
resulting in a spin-velocity magnitude near to 20\,Km/s. In this case the spin
angle over the $xy$ plane have values near to $290^{\circ}$ and the
corresponding polar angle correspond to values near to $153^{\circ}$.
%
Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.
% %%%%%%%%%%%%%%%%
% %% Description of ALT |V^{y}|, components and RTP
% %%%%%%%%%%%%%%%%
Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, we notice that this
response is almost two times more intense than $|\mathcal{V}^{\mathrm{x}}|$. For
the energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more
intense response than $yx$ and $yy$ components. This results in a spin azimuthal
angle near to $221^{\circ}$ and polar angle near to $141^{\circ}$.
%
For the energy range all three components have
almost the same intensity resulting in a spin-velocity near to 50\,Km/s in both
cases.
%
Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
the same spin polarization for all this range.}
